---
title: "EyeTracking"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(magrittr)
library(eyelinker)
library(purrr)
library(ivs)
```

\section{Try with a new package}
```{r}
asc <- read.asc('83.asc')
str(asc, max.level = 1)
msg <- asc$msg
button <- asc$button
sacc <- asc$sacc
```

\section{Button}
Transform the `button` data frame to keep only periods when the target is presented (not the fixation) and only trials that are "easy" to interperet. By "easy" I mean there are exactly 4 times when the button changes state: On Fixation -> Off Fixation -> On Target -> Off Target.
Creates `button_w` a wide data frame that has each trial and the stimulus onset `stimS` and stimulus disappearance `stimE`.
```{r ButtonTransformation}
button %<>% group_by( # Keep only 'easy' trials with the expected number of buttons
  block) %>% mutate(nPer=n()) %>% ungroup() %>% subset(nPer == 4)
button$stim <- c('fix','fix','target','target') %>% rep(nrow(button)/4) %>% c() # What is presented
button %<>% subset(stim == 'target') # Keep only target
button_w <- button %>% 
  group_by(block) %>% 
  arrange(time, .by_group = TRUE) %>% 
  mutate(stimS = min(time), stimE = max(time)) %>% 
  ungroup() %>% 
  select(c('block','button','stim','stimS','stimE')) %>% 
  distinct()
```
\section{Interal Vectors}
Set internal vectors (IVs) using the `ivs` package. Vectors will allow easy indexing to see which saccades take place in which stimulus period.
```{r IVs}
sacc_IVs <- iv(sacc$stime,sacc$etime)
button_IVs <- iv(button_w$stimS,button_w$stimE)
locations <- iv_locate_overlaps(sacc_IVs,button_IVs)
IV_indexing <- locations[!is.na(locations$haystack),]

# Index the button_w df based on the index values of IV_indexing$haystack
button_w_saccade <- button_w[IV_indexing$haystack,]
saccade_w_button <- sacc[IV_indexing$needles,]
```
\section{Subset `msg`}
```{r msgDF}
blocks <- saccade_w_button$block
msg_w_saccades <- msg[which(msg$block %in% blocks),]
msg_w_saccades <- msg_w_saccades[which(grepl("TRIAL_START",msg_w_saccades$text)),]

split_cols <- do.call(rbind, strsplit(msg_w_saccades$text, " | ", fixed = TRUE))
msg_w_saccades$trialN    <- split_cols[, 1]
msg_w_saccades$Condition <- split_cols[, 2]
msg_w_saccades$TC        <- split_cols[, 3]
msg_w_saccades$trialN %<>% gsub("TRIAL_START ", '', .)

msg_w_saccades <- subset(msg_w_saccades, !endsWith(Condition,"_null"))
msg_w_saccades$CondShort <- car::recode(msg_w_saccades$Condition, recodes = 
                         "'FarHighNarrow' = 'IN'; 'FarLowNarrow' = 'DN';
                        'FarHighWide' = 'IW'; 'FarLowWide' = 'DW';
                        'ThreeLinesControl' = 'Single'; 'Constant' = 'Constant'") %>% as.factor()
```

Create the final data frame. But first we must refilter each data frame so it only includes the correct trials.
```{r dfFull}
# Step 1: Find common block values
common_blocks <- reduce(
  list(
    button_w_saccade$block,
    saccade_w_button$block,
    msg_w_saccades$block
  ),
  intersect
)

# Step 2: Filter all data frames
button_w_saccade_filt <- button_w_saccade %>% filter(block %in% common_blocks)
saccade_w_button_filt <- saccade_w_button %>% filter(block %in% common_blocks)
msg_w_saccades_filt   <- msg_w_saccades   %>% filter(block %in% common_blocks)
```
Then we must reduce the number of rows in the saccade df by taking summary stats.
```{r}
saccadeFinal <- saccade_w_button_filt %>% group_by(block) %>% 
  mutate(nSaccades = n(), 
         meamAmplitude = mean(ampl), 
         meanPeakVelocity = mean(pv), 
         meanDuration = mean(dur)) %>% 
  select(nSaccades,meamAmplitude,meanPeakVelocity,meanDuration,block) %>% 
  ungroup() %>% 
  distinct()
```

```{r}
# Step 3: Combine them row-wise
all_data <- cbind(saccadeFinal,msg_w_saccades[c(4,5,6,7)])
dataByCondition <- all_data %>% group_by(CondShort) %>% 
  mutate(nTrialsWithSaccade = n(),
         grandMeanAmp = mean(meamAmplitude, na.rm = TRUE),
         grandMeanVel = mean(meanPeakVelocity, na.rm = TRUE),
         grandMeanDurt = mean(meanDuration, na.rm = TRUE),
         meanSaccades = mean(nSaccades, na.rm = TRUE)) %>% 
  select(nTrialsWithSaccade,meanSaccades,grandMeanVel,grandMeanDurt,grandMeanAmp,CondShort) %>% 
  ungroup() %>% 
  distinct()
```