---
title: "AnalysisRaw7LS"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(dplyr)
library(car)
library(ggplot2)
library(ggpubr)
library(ggpattern)
library(ggsignif)
library(viridis)
library(xtable)
library(lme4)
library(lmerTest)
library(afex)


dfFull <- read.csv("glmDataRaw7LS.csv")
dfFull$CondShort %<>% as.factor
dfMean <- read.csv('subjectMeansByTCFactorRaw7LS.csv')
dfMean$CondShort %<>% as.factor
dfOverallMean <- read.csv('subjectMeansOverallRaw7LS.csv')
dfOverallMean$CondShort %<>% as.factor

```

\section{Stats}
\subsection{Perform GLM:}
  Model the GLM with the coding scheme of Condition comparing the different levels of Condition against the control group `ThreeLinesControl`.
  We used to compare multiple GLMs. The two GLMs would use either 'Target' or 'Straight' as the comparison group. However the rest of the GLM statistics except for p-value would be identical. It makes more sense to use just use one effects-coded model and then emmeans later.
  
\subsection{Perform Likelihood Ratio Test (LRT):}
  The LRT assesses the impact of the predictors. It compares the model w/ the predictor (each row of the output) to a model w/out that predictor. The columns included the Likelihood-Ratio against a Chi-squared distribution (LR Chisq), the degrees of freedom (DF), and the P-value against the Chi-squared distribution (Pr(>Chisq)). A significant value indicates that inclusion of that parameter is significantly improving the overall model fit.
  
\subsection{Confidence Intervals}
  CI's are estimated using the Profile-based method. This essentially is measuring the derivative of the probability density function. When the PDF in/decreases rapidly enough, the that is where the CI is estimated to be.
```{r} 
#### Perform GLM ####
conds <- levels(dfFull$CondShort)
Formula <- "Correct_Response ~ TC_michelson_c * CondShort + (1|Participant_Number)"
Contrasts <- list(CondShort = contr.treatment(conds, which(conds == 'Single')))
model_glm <- glmer(
  formula = Formula,
  family = binomial(link='logit'),
  data = dfFull,
  contrasts = Contrasts,
  weights = weights,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e5),
                         check.conv.grad = .makeCC("warning", tol = 0.005, relTol = NULL)),
)
dfFull$probability <- predict(model_glm,type='response', re.form = NA) # re.form=NA is fixed effects only. =NULL is both

# Likelihood Ratio test
#model_LRT <-  car::Anova(model_glm,type = 3, test.statistic = 'LR')
model_LRT <- afex::mixed(
  formula = Formula,
  data = dfFull,
  family = binomial(link = 'logit'),
  method = "LRT",  # Type III tests via LRT
  type = 3,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e5),
                         check.conv.grad = .makeCC("warning", tol = 0.005, relTol = NULL))
)
# CI's #
model_CIs <- lme4::confint.merMod(model_glm, method = 'Wald', parm = 'beta_')
```

```{r LaTexPart1, include=FALSE}
# Make the output DF better and Print it #
model_df <- broom.mixed::tidy(model_glm,effects='fixed') %>% as.data.frame()
model_df <- model_df[-1]
model_df %<>% cbind(.,exp(model_CIs))
model_df %<>%  tibble::add_column('Odds Scale'= exp(model_df$estimate), .after = 2)

model_df$term %<>% gsub("CondShort","",.)
model_df$term %<>% gsub("_michelson_c","",.)
rownames(model_df) <- model_df$term
model_df <- model_df[-1]

newCols <- c('Est.','Odds','SE','z','p','2.5\\%','97.5\\%')
colnames(model_df) <- newCols

for (col in colnames(model_df)){
  model_df[[col]] %<>% sprintf("%.2e",.)
}

model_df %>% xtable(
  auto = TRUE,
  align = c('l','r','r','r','r','r','r','r'),
  digits = 3,) %>% 
  print(
    include.rownames = T,
    type = 'latex',
    file = "/Users/harrysteinharter/Documents/LaTex/ThesisV2/tables3/Exp3GLM.tex",)
## LRT printing ##
LRT_print <- model_LRT %>% as.data.frame()
rownames(LRT_print) %<>% gsub("_michelson_c","",.)
LRT_print$`Pr(>Chisq)` %<>% sprintf("%.2e",.)
print(
  xtable(
    LRT_print,
    align = c('l','r','r','r'),
    auto = TRUE,
    label = "table:Exp3LRT",
    caption = c("Caption Here","Exp 3: LRT"),
    digits = 2
    ),
  include.rownames = T,
  type = 'latex',
  file = "/Users/harrysteinharter/Documents/LaTex/ThesisV2/tables3/Exp3LRT.tex",
)
```
\subsection{Pairwise comparisons}
Now we will use `emmeans::emmeans()` to perform pairwise comparisons between conditions.
```{r}
model_TC <- lmer(
  data = dfFull,
  formula = "TC_michelson_c ~ WidthGroup*ExpectedGroup + (1|Participant_Number)",
  weights = weights
)
model_EM <- emmeans::emmeans(model_TC, specs = ~ExpectedGroup*WidthGroup, type = 'response', pbkrtest.limit = 1e5)
AnovaTC <- Anova(model_TC,type=3)
EM_pairs <- pairs(model_EM)
EM_pairs_df <- EM_pairs %>% as.data.frame()
```

```{r LaTexPart2, include=F}
#### Now format the printing of the Anova and Emmeanns
colnames(EM_pairs_df) <- c('Comparison','Est.','SE','df','t-ratio','p')
EM_pairs_df$Comparison %<>% gsub("low","D",.)
EM_pairs_df$Comparison %<>% gsub("high","I",.)
EM_pairs_df$Comparison %<>% gsub("wide","W",.)
EM_pairs_df$Comparison %<>% gsub("narrow","N",.)
EM_pairs_df$Comparison %<>% gsub("D controls","Single",.)
EM_pairs_df$Comparison %<>% gsub("I controls","Constant",.)
EM_pairs_df$Comparison %<>% gsub(" ","",.)
EM_pairs_df$Comparison %<>% gsub("-"," - ",.)
EM_signif_df <- subset(EM_pairs_df, p <= 0.05)

for (i in c(2,3,6)){
  EM_pairs_df[[i]] %<>% sprintf("%.2e",.)
  EM_signif_df[[i]] %<>% sprintf("%.2e",.)
}
EM_pairs_df$`t-ratio` %<>% sprintf("%.2f",.)
EM_signif_df$`t-ratio` %<>% sprintf("%.2f",.)

sink("/Users/harrysteinharter/Documents/LaTex/ThesisV2/tables3/Exp3Pairwise.tex")
EM_pairs_df %>% xtable(
  align = c('c','l','r','r','r','r','r'),
  label = "table:Exp3Pairwise",
  caption = c("Caption Here","Exp 3: Pairwise"),
) %>% print(
  type = 'latex',
  include.rownames = F,)
sink("/Users/harrysteinharter/Documents/LaTex/ThesisV2/tables3/Exp3PairwiseSignif.tex")
EM_signif_df %>% xtable(
  align = c('c','l','r','r','r','r','r'),
  label = "table:Exp3PairwiseSignif",
  caption = c("Caption Here","Exp 3: PairwiseSignif"),
) %>% print(
  type = 'latex',
  include.rownames = F,)
sink()
```

```{r aesthetics, include=FALSE}
cV <- viridis(2, option = 'viridis')
colorPalette <- c('high' = cV[1], 'low' = cV[2])
colorPalette <- c('high' = 'firebrick', 'low' = 'dodgerblue')
palette3Way <- viridis(conds %>% length())
palette3Way %<>% setNames(.,conds)
```

```{r curvesplot, echo=FALSE}
ggplot(data = dfFull,
       mapping = aes(x = TC_michelson, color = ExpectedGroup)
) + geom_line(
  mapping = aes(y = probability, linetype = WidthGroup),
  linewidth = 1.0
) + geom_jitter(
  mapping = aes(y = performance, shape = WidthGroup),
  alpha = I(.1),
  size = I(.7),
  height = 0.05,
  width = NULL,
  show.legend = FALSE
) + scale_x_continuous(
  transform = 'log10'
) + scale_linetype_manual(
  name = 'Conditions',
  values = c(
    'controls' = 'solid',
    'narrow' = 'twodash',
    'wide' = 'dotted'
  ),
  labels = c('Controls','Narrow','Wide')
) + scale_color_manual(
  values = colorPalette,
  name = "Contrast",
  labels = c('Increasing', 'Decreasing')
) + xlab(
  'Target Contrast'
) + ylab(
  'Probability of Detection'
) + theme_pubr(
) + theme(
  legend.title = element_text(hjust = .5, vjust = .5),
  text = element_text(size=16,family='times'),
  legend.position = 'right'
)

ggsave(
  filename = "/Users/harrysteinharter/Documents/LaTex/ThesisV2/images3/Exp3GLM.png",
  units = 'in',
  dpi = 500,
  width = W <- 8,
  height = W * (2/3)
  )

```

Bar plot to compare mean `TC_michelson` across `Condition`.
```{r barplot, echo = FALSE}
ggplot(
  data = dfOverallMean,
  mapping = aes(x = factor(CondShort, c('Constant','IN','IW','Single','DN','DW')), 
                y = overall_mean, group = WidthGroup, linetype = WidthGroup)
) + stat_summary(
  mapping = aes(color = ExpectedGroup, shape = WidthGroup),
  geom = 'point',
  fun = 'mean',
  size = I(5),
) + stat_summary(
  geom = 'errorbar',
  fun.data = mean_cl_normal,
  position = position_dodge(width = 0.9), 
  width = 0.2,
  linetype = I('solid')
) + scale_color_manual(
  values = colorPalette,
  name = "Contrast",
  labels = c('Increasing', 'Decreasing')
) + scale_shape_manual(
  name = 'Conditions',
  values = c(
    'controls' = 15,
    'narrow' = 16,
    'wide' = 17),
  labels = c('Controls','Narrow','Wide')
) + scale_x_discrete(
   labels = c('Constant','IN','IW','Single','DN','DW')
) + theme_pubr(
) + theme(
  legend.title = element_text(hjust = .5, vjust = .5),
  text = element_text(size=16,family='times'),
  legend.position = 'right'
) + ylab(
  "Mean Target Contrast"
) + xlab(
  "Condition"
)

ggsave(
  filename = "/Users/harrysteinharter/Documents/LaTex/ThesisV2/images3/Exp3AnovaPlot.png",
  units = 'in',
  dpi = 500,
  width = W <- 8,
  height = W * (2/3)
  )
```

Now we want to see if there's a "Stronger interaction w/ weak stimuli". So we can test this by binning `TC_michelson_c` into 3 groups: `low`, `med`, `high`. We can then test for a 3-way interaction between TC:Contrast:Condition. Depending on the presence or absence of an interaction, and graphical interpretation to see directionality, we can say whether or not the 2-way interaction between `WidthGroup` and `ExpectedGroup` is stronger w/ a weak stimulus. `TC_factor` already exists from the beginning.
Absence of a 3-way interaction indicates that the 2-way interaction is not modulated by the 3rd predictor. I.E., \textit{there is \textbf{NO} stronger interaction w/ weak stimuli}.
```{r 3WayIntrxn}
model3way <- lmer(
  data = dfFull,
  formula = "Correct_Response ~ TC_factor * WidthGroup * ExpectedGroup + (1|Participant_Number)",
)
anova3way <- Anova(model3way,type = 3)
model_EMx3 <- emmeans::emmeans(model3way, specs = ~ExpectedGroup*WidthGroup|TC_factor, 
                               type = 'response', pbkrtest.limit = 1e5)
EM_pairs_x3 <- pairs(model_EMx3)
EM_pairs_df_x3 <- EM_pairs_x3 %>% as.data.frame()
EM_signif_df_x3 <- subset(EM_pairs_df_x3, p.value <= .05)
```
```{r plot3way, echo=F}
ggplot(
  data = dfMean,
  mapping = aes(
    x = factor(TC_factor,c('Low','Medium','High')), y = mean, 
    color = ExpectedGroup, shape = WidthGroup, 
    group = interaction(ExpectedGroup,WidthGroup))) + 
  stat_summary(
    geom = 'point',
    fun.data = mean_cl_normal,
    position = position_dodge(.75),
    size = I(5),) + 
  stat_summary(
    geom = 'errorbar',
    fun.data = mean_cl_normal,
    position = position_dodge(.75), 
    width = 0.2,
    linetype = I('solid'),
    color = 'black') +
  scale_color_manual(
    values = colorPalette,
    labels = c('Increasing','Decreasing'),
    name = 'Contrast') +
  scale_shape_manual(
    values = list(
      'controls' = 15,
      'narrow' = 16,
      'wide' = 17),
    labels = c('Controls','Narrow','Wide'),
    name = 'Condition') +
  theme_pubr() + 
  theme(
    legend.position = 'right',
    legend.title = element_text(hjust = .5, vjust = .5),
    text = element_text(family = 'times', size = 16)) +
  xlab('Target Contrast') + ylab('Mean Response Rate') +
  guides(
    color = guide_legend(order = 1),
    shape = guide_legend(order = 2))
  
ggsave(
  filename = "/Users/harrysteinharter/Documents/LaTex/ThesisV2/images3/Exp3Anova3Way.png",
  units = 'in',
  dpi = 500,
  width = W <- 8,
  height = W * (2/3)
  )
```

